%*****************************************
\chapter*{Forward}\label{for:forward}
%*****************************************
%TODO Reviewed

I have taught BASV 316, \textit{Introductory Methods of Analysis}, online for the University of Arizona in Sierra Vista since 2010 and enjoy working with students on research methodology. From the start, I wanted students to work with statistics as part of our studies and carry out the types of calculations that are discussed in the text. As I evaluated statistical software I had three criteria:

\begin{itemize}
  \item \textbf{Open Educational Resource (OER)}. It is important to me that students use software that is available free of charge and is supported by the entire web community. 
  \item \textbf{Platform}. While most of my students use a Windows-based system, some use Macintosh and it was important to me to use software that is available for all of those platforms. As a bonus, most OER software is also available for the Linux system, though I'm not aware of any of my students who are using Linux.
  \item \textbf{Longevity}. I wanted a system that could be used in other college classes or in a business setting after graduation. That way, any time a student spends learning the software in my class will be an investment that can yield results for many years.
\end{itemize}

I originally wrote a series of six lab exercises (later expanded to nine) using R-Project since that software met these three criteria. Moreover, R-Project is a recognized standard for statistical analysis and could be easily used for even peer-reviewed published papers. Unfortunately, I found R-Project to be confusing to students since it is text-based with rather complex commands. I found that I spent a lot of time just teaching students how to set up a single test with R-Project instead of analyzing the result. In the spring of 2017 I changed to \texttt{SOFA} (\textit{Statistics Open For All}) because it is much easier to use and still met my criteria.

This lab manual explores every aspect of \texttt{SOFA} in a series of ten lab exercises plus a final. It is my hope that students will find the labs instructive and will then be able to use \texttt{SOFA} for other classes. This lab manual is published under a Creative Commons license with a goal that other instructors will modify it to meet their own needs. I always welcome comments and will improve this manual as I receive feedback.

\bigskip
\begin{flushright}
  \textemdash  George Self
\end{flushright}


